---
title: "Exploratory Data Analysis"
output: rmarkdown::github_document
      
---
Data comes from here: https://www.goodreads.com/list/show/50.The_Best_Epic_Fantasy

```{r include = FALSE}
library(dplyr)
library(magrittr)
library(ggplot2)
library(RColorBrewer)
library(quanteda)
bestEpicFantasy<-read.csv('https://raw.githubusercontent.com/connorH982/projects/master/GoodreadsProject/bestEpicFantasy.csv',header = TRUE)
```

## Wordclouds

### Wordcloud of the book titles

```{r}
############# TITLE WORDCLOUD #############################################
# Create corpus
title.corpus<-corpus(as.character(bestEpicFantasy$title))

# now creating a document-feature matrix using dfm()
T.plot<-dfm(title.corpus, tolower = TRUE, remove_punct = TRUE, remove_twitter = TRUE, remove_numbers = TRUE, remove=stopwords(source = "smart"))

# Colors
T.col <- brewer.pal(10, "BrBG")  

# Create Wordcloud
textplot_wordcloud(T.plot, min_count = 16, color = T.col)
```

### Wordcloud of the book descriptions

```{r}
############# DESCRIPTIONS WORDCLOUD #############################################
# Create corpus
descriptions.corpus<-corpus(as.character(bestEpicFantasy$book.descriptions))

# now creating a document-feature matrix using dfm()
D.plot<-dfm(descriptions.corpus, tolower = TRUE, remove_punct = TRUE, remove_twitter = TRUE, remove_numbers = TRUE, remove=stopwords(source = "smart"))

# Colors
D.col <- brewer.pal(10, "BrBG")  

# Wordcloud
textplot_wordcloud(D.plot, min_count = 16, color = D.col)  
```

## Numerical Analysis

### Total Ratings: Histogram and Boxplot

```{r}
ggplot(data = bestEpicFantasy, aes(log(bestEpicFantasy$total_ratings)))+
  geom_histogram(bins = 25,fill="dodgerblue4")+
  labs(title="Histogram for Total # of Reviews")+
  labs(x="Log Total Reviews",y="Counts")


ggplot(data = bestEpicFantasy, aes(y=bestEpicFantasy$total_ratings,x=""))+
  geom_boxplot(fill="dodgerblue4",width=0.1)+
  labs(title="Boxplot for Total Ratings")+
  labs(y="Total # of Ratings",x="")

#Outlier: It is Harry Potter book 1 (no surprise there)
bestEpicFantasy[which.max(bestEpicFantasy$total_ratings),c("title","total_ratings","book.descriptions")]
```

### Pages: Histogram and Boxplot

```{r}
#################### PLOT Pages #########################################

pageplt<-ggplot(data = bestEpicFantasy, aes(bestEpicFantasy$pageCounts))+
  geom_histogram(bins = 25,fill="dodgerblue4")+
  labs(title="Histogram for Page Lengths")+
  labs(x="Total Pages",y="Counts")
pageplt

ggplot(data = bestEpicFantasy, aes(y=bestEpicFantasy$pageCounts,x=""))+
  geom_boxplot(fill="dodgerblue4",width=0.1)+
  labs(title="Boxplot for Page Lengths")+
  labs(y="Page Lengths",x="")
```

### Average Ratings: Histogram and Boxplot

```{r}
################### PLOT Average Ratings ###################################

avgplt<-ggplot(data = bestEpicFantasy, aes(bestEpicFantasy$average_rating))+
  geom_histogram(bins = 25,fill="dodgerblue4")+
  labs(title="Histogram for Average Ratings")+
  labs(x="Average Rating",y="Counts")
avgplt

ggplot(data = bestEpicFantasy, aes(y=bestEpicFantasy$average_rating,x=""))+
  geom_boxplot(fill="dodgerblue4",width=0.1)+
  labs(title="Boxplot for Average Ratings")+
  labs(y="Average Rating",x="")
```

## Categorical Data

### Awards/Nominations: Barplot

```{r}
#######################PLOT Award ########################################

awardplt<-ggplot(data=bestEpicFantasy,aes(bestEpicFantasy$hasAward))+geom_bar(fill="dodgerblue4")
awardplt
```

### Genres: Barplot

Almost all books in this set are tagged Fantasy, with a large number of other genres with very few titles. Therefore I relabeled these rarer genres as "Other genres" for presentation and testing.

```{r}
######################PLOT Genres ###########################################

tp <- bestEpicFantasy
levels(tp$genreVoted)[levels(tp$genreVoted) != "Fantasy"] <- "Other Genres"

genreplt<-ggplot(data = tp,aes(x = genreVoted))+geom_bar(fill="dodgerblue4")+
  labs(title = "Histogram for Genres")+
  labs(x = "Genre 'tagged' by vote on GoodReads.com", y = "Count")
genreplt

```

## Crossing Variables and Statistical Testing

### Genres and Awards: CHI-SQ

```{r}
############# CROSS Genres With Awards###################################
# Outcome: SUCCESSFULLY reject Null Hypothesis
crossplt<-ggplot(data = tp,aes(x = genreVoted, fill = hasAward))+geom_bar(position = "dodge")+
  labs(title = "Genres crossed with Awards")+
  labs(x = "Genre", y = "Count")+
  scale_fill_discrete("Has Award/Nom")
crossplt

# Same plot but if we wanted to exclude NA cases
tpNoNA<-tp[complete.cases(tp),]
tbl<-table(tpNoNA$genreVoted, tpNoNA$hasAward)
chisq.test(tbl)

crossplt2<-ggplot(data = tpNoNA,aes(x = genreVoted, fill = hasAward))+geom_bar(position = "dodge")+
  labs(title = "Genres crossed with Awards (excluding NAs)")+
  labs(x = "Genre", y = "Count")+
  scale_fill_discrete("Has Award/Nom")
crossplt2
```

### Average Rating with Genre: Kruskal-Wallis

```{r}
############# CROSS Genres With Average Ratings###################################
# Outcome: Close... can reject the null hypothesis at 0.05 confidence threshold.

avgGenrePlt<-ggplot(data = tp,aes(x = genreVoted, y = average_rating))+geom_boxplot(fill="dodgerblue4", width=0.1)+
  labs(title = "Genres By Ratings")+
  labs(x = "Genre", y = "Ratings")
avgGenrePlt

kruskal.test(average_rating~genreVoted,data = tp)
tblResults<-with(tp,tapply(average_rating,genreVoted,median))
tblResults
```

### Page Lengths with Genre: Kruskal-Wallis

```{r}
############# CROSS Genres With Page Counts###################################
# Outcome: SUCCESSFULLY reject Null hypothesis

pageGenrePlt<-ggplot(data = tp,aes(x = genreVoted, y = pageCounts))+geom_boxplot(fill="dodgerblue4",width=0.1)+
  labs(title = "Genres By Pages")+
  labs(x = "Genre", y = "Page Length")
pageGenrePlt

kruskal.test(pageCounts~genreVoted,data = tp)
```

### Average Rating with Award/Nomination: Kruskal-Wallis

```{r}
############# CROSS Award With Average Ratings###################################
#Outcome: FAIL to reject null

avgGenrePlt<-ggplot(data = tp,aes(x = hasAward, y = average_rating))+geom_boxplot(fill="dodgerblue4", width=0.1)+
  labs(title = "Awards/Nominations By Ratings")+
  labs(x = "Award/Nominations", y = "Ratings")
avgGenrePlt

kruskal.test(average_rating~hasAward,data = tp)
```

### Total Ratings with Award/Nomination: Kruskal-Wallis

```{r}
############# CROSS Awards With Total Numbers of Reviews ###################################
#Outcome: SUCCESSFULLY reject Null
pageGenrePlt<-ggplot(data = tp,aes(x = hasAward, y = total_ratings))+geom_boxplot(fill="dodgerblue4",wdith=0.1)+
  labs(title = "Award/Nomination By Total Ratings")+
  labs(x = "Award", y = "Total Ratings")
pageGenrePlt

kruskal.test(total_ratings~hasAward,data = tp)
tblResults<-with(tp,tapply(total_ratings,hasAward,median))
tblResults
```
